Dissertation

### 2023-10-17 Manuscript/manuscript.qmd
remove redundancies

## Procedure
Upon arrival at the laboratory, participants were provided with a description of the experiment and signed informed consent forms. They were then seated in front of a computer equipped with a mouse and were given instructions on how to perform the "Hit The Wall" (HTW) visuomotor extrapolation task.

>>>>

## Procedure
